Unshuffling Permutations

### 2015-09-14 article.tex
abstract

\begin{abstract}
bla bla bla \ldots
\end{abstract}

@@

>>>>

\begin{abstract}
  A permutation is said to be a square if it is the union of two order-isomorphic
  patterns.
  The definition is intended to be the natural counterpart to the ordinary shuffle
  of words and languages.
  In this paper, we tackle the problem of recognising square permutations from both
  the point of view of algebra and algorithmic.
  On the one hand, we present some algebraic properties of the shuffle product of
  permutations and exhibit a bijection between square $(213,231)$-avoiding permutations
  and square binary words.
  On the other hand, we prove that recognising square permutations is \NPC.
\end{abstract}

@@

$123$-avoiding (resp. $321$-avoiding) permutations are the union of two decreasing
(resp. incresing) patterns.
